A flexible integer linear programming formulation for scheduling clinician on-call service in hospitals

### 2019-10-09 paper/paper.experiments.tex
Minor fixes in abstract/acks/experiments
Add citation for scheduling repo

\subsection{Implementation}
We developed a Python software package with a user interface that implements the above
linear program and allows configuration of clinicians at~\cite{...}, to be
% JK: what is this ref? Do you want to mention it is in Python?
% TODO: I will add a ref to our Github repo here, once I clean it up and open source it
used by the ID division at St.\ Michael's Hospital. The software was used to
generate the results in the following sections, using real data as well as
simulated data as input. All the following experiments were conducted on an
Intel Core i7-4770k CPU @ 3.50 GHz with 16 GB of RAM running 64-bit Windows 10.
Our software package uses COIN-OR Branch-and-Cut open source solver
% JK: "software" here is not clear to me, is it the solver for the ILP formulation?
version 2.9.9~\cite{johnjforrest_coin-or/cbc:_2019}.

>>>>

\subsection{Implementation}
We developed a Python software package with a user interface that implements the above
linear program and allows configuration of clinicians, to be
% JK: what is this ref? Do you want to mention it is in Python?
used by the ID division at St.\ Michael's Hospital~\cite{landsman_scheduling}. 
The software was used to
generate the results in the following sections, using real data as well as
simulated data as input. All the following experiments were conducted on an
Intel Core i7-4770k CPU @ 3.50 GHz with 16 GB of RAM running 64-bit Windows 10.
Our software package uses COIN-OR Branch-and-Cut open source solver
% JK: "software" here is not clear to me, is it the solver for the ILP formulation?
version 2.9.9~\cite{johnjforrest_coin-or/cbc:_2019}.
